Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Modify Component

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.

@@

\subsubsection{Masked Authenticated Messaging}
MAM\cite{MAM} is one of the best features of IOTA, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network. The consensus algorithm of IOTA ensures data integrity. These properties allow MAM to meet the requirements of both data integrity and privacy.

IOTA only allows one message per transaction and couldn't publish continuous related messages because it is easy for an attacker to issue spam transactions if the same address is used. However, MAM publishes each message to a different addresses, and each can be derived from the previous one, this mechanism protects the channel from spamming and allows us to have access to all information with channel root only. Furthermore, MAM can be used in 3 ways to control visibility and access which are public, restricted and private. In our system, restricted MAM channel is used to achieve data authoriazation between providers and consumers.

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication. With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.

\subsubsection{Blind Signature}
Blind signature\cite{blindSig} is a form of digital signature where the message is blinded before it is signed, and the resulting blind signature can be verified publicly against the original. To perform such a signature, the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to upload the secret key of MAM channel to smart contract without knowing it. Furthermore, only one blind-signatured secret key is valid for trading and it is not allowed to be updated. By putting the secret key on smart contract prevents malicious providers trades invalid secret keys to consumers privately.

>>>>

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.

@@
